---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edar

<!-- badges: start -->
[![R-CMD-check](https://github.com/degiwo/edar/workflows/R-CMD-check/badge.svg)](https://github.com/degiwo/edar/actions)
<!-- badges: end -->

The goal of edar is to provide easy to use functions for explorative data analysis with R.

## Installation

You can install the development version of edar like so:

``` r
# install.packages("devtools")
devtools::install_github("degiwo/edar")
```

## Example

This is a basic example which shows you how to use the package:

```{r example}
library(edar)
edar()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
